REDO Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution I: Methods and Test Case

### 2017-11-16 main.tex
Update on Overleaf.

\begin{figure}
\includegraphics[width=0.9\linewidth]{species_bar.png}\\
\includegraphics[width=0.9\linewidth]{species_bar_disk.png}
\caption{The fraction of each species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone each in phase of the ISM (bottom).}
\label{fig:species_fractions}
\end{figure}

@@

\subsection{Stellar Abundances}
\label{sec:stellar properties}
We plot the $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ ratio for all star particles in our simulation that are ``alive'' in Figure~\ref{fig:stellar_abundance}. This represents stars that have not gone supernovae or have otherwise formed a compact object. Here, $\alpha = (\rm{O} + \rm{Mg} + \rm{Si})/3.0$, and the notation [X/Y] denotes the ratio of the abundance of species X over Y, relative to the solar value, or log([X/Y]) = log(X/Y) - log(X$_{\odot}$/Y$_{\odot}$). All stars are colored by their age.

>>>>

\begin{figure*}
\includegraphics[width=0.9\linewidth]{species_bar.png}\\
\includegraphics[width=0.9\linewidth]{species_bar_disk.png}
\caption{The fraction of each species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone each in phase of the ISM (bottom).}
\label{fig:species_fractions}
\end{figure*}

@@

\subsection{Stellar Abundances}
\label{sec:stellar properties}
\textbf{This section needs work. As per discussion with Keith and Kathryn, displaying abundance evolution like this is confusing and misleading. Switch to discussion of mass / abundance fraction evolution of individual specie(s).}
We plot the $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ ratio for all star particles in our simulation that are ``alive'' in Figure~\ref{fig:stellar_abundance}. This represents stars that have not gone supernovae or have otherwise formed a compact object. Here, $\alpha = (\rm{O} + \rm{Mg} + \rm{Si})/3.0$, and the notation [X/Y] denotes the ratio of the abundance of species X over Y, relative to the solar value, or log([X/Y]) = log(X/Y) - log(X$_{\odot}$/Y$_{\odot}$). All stars are colored by their age.
